MVT Normal: wide

### 2020-10-22 src/s_cauchy.Rmd
small changes

laccuracy <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="xgbTree"))

@@

laccuracy1 <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="xgbTree"))

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_xgbtree.rds")
```

@@

Add in GBM R*
```{r}
a_df <- readRDS("../output/cauchy_r_star_xgbtree.rds") %>% 
  mutate(model="gbm")
a_df1 <- readRDS("../output/cauchy_r_star_rf.rds") %>% 
  mutate(model="rf")
g2 <- a_df %>%
  bind_rows(a_df1) %>% 
  melt(id.vars=c("iteration", "model")) %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable), linetype=as.factor(model))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))+
  scale_linetype_discrete("Model") +
  guides(colour = guide_legend(nrow = 1, byrow = T),
         linetype=guide_legend(nrow = 1, byrow = T))
ggsave("../output/fig_9d.pdf", g2, width = 12, height = 8)
```

>>>>

laccuracy <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="gbm"))

@@

laccuracy1 <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="gbm"))

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_gbm.rds")
```

@@

Add in GBM R*
```{r}
a_df <- readRDS("../output/cauchy_r_star_gbm.rds") %>% 
  mutate(model="gbm")
a_df1 <- readRDS("../output/cauchy_r_star_rf.rds") %>% 
  mutate(model="rf")
g2 <- a_df %>%
  bind_rows(a_df1) %>% 
  melt(id.vars=c("iteration", "model")) %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable), linetype=as.factor(model))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))+
  scale_linetype_discrete("Model") +
  guides(colour = guide_legend(nrow = 1, byrow = T),
         linetype=guide_legend(nrow = 1, byrow = T))
ggsave("../output/fig_9d.pdf", g2, width = 12, height = 8)
```

### 2020-10-22 src/s_wide_distributions.Rmd
small changes

full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star <- r_star_dist(full_data)

a_df <- tibble(samples_cp=r_star)

@@

Non-centered
```{r}
# A <- readRDS("../output/A_matrix.rds")
# model <- stan_model("mvt_250_ncp.stan")
# fit <- sampling(model, data=list(N=N, A=A), iter=500, chains=4, thin=1)
# saveRDS(fit, "../output/mvt_ncp_fit_500.rds")
fit <- readRDS("../output/mvt_ncp_fit_500.rds")
full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star <- r_star_dist(full_data)

a_df <- a_df %>%
  mutate(samples_ncp=r_star)
# saveRDS(a_df, "../output/mvt_500_all.rds")
a_df <- readRDS("../output/mvt_500_all.rds")
g <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("Centered", "Non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=20, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("A.")
# ggsave("../output/wide_data.pdf", g, width = 12, height = 8)

@@

full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star <- r_star_dist(full_data)
a_df <- tibble(samples_400=r_star)
# saveRDS(a_df, "../output/mvt_wide_400_summary.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
```

@@

fit <- readRDS("../output/mvt_wide_1000.rds")
full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star1 <- r_star_dist(full_data)

a_df <- a_df %>%
  tibble(samples_1000=r_star1)
saveRDS(a_df, "../output/mvt_wide_summaries.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
a_df <- readRDS("../output/mvt_wide_summaries.rds")
a_df <- tibble(samples_400=a_df$.$samples_400, samples_1000=a_df$samples_1000)
g1 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400", "1000")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=20, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")
ggsave("../output/very_wide_data.pdf", g, width = 12, height = 8)
```

>>>>

full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star_gbm <- r_star(full_data, uncertainty = T, method="gbm")
r_star_rf <- r_star(full_data, uncertainty = T, method="rf")

a_df <- tibble(samples_cp_gbm=r_star_gbm,
               samples_cp_rf=r_star_rf)

@@

Non-centered
```{r}
# A <- readRDS("../output/A_matrix.rds")
# model <- stan_model("mvt_250_ncp.stan")
# fit <- sampling(model, data=list(N=N, A=A), iter=500, chains=4, thin=1)
# saveRDS(fit, "../output/mvt_ncp_fit_500.rds")
fit <- readRDS("../output/mvt_ncp_fit_500.rds")
full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star_gbm <- r_star(full_data, uncertainty = T, method="gbm")
r_star_rf <- r_star(full_data, uncertainty = T, method="rf")

a_df <- a_df %>%
  mutate(samples_ncp_gbm=r_star_gbm,
         samples_ncp_rf=r_star_rf)
saveRDS(a_df, "../output/mvt_500_all.rds")
a_df <- readRDS("../output/mvt_500_all.rds")
a_df_gbm <- a_df %>%
  select(contains("gbm")) %>% 
  rename(samples_cp=samples_cp_gbm,
         samples_ncp=samples_ncp_gbm) %>% 
  mutate(Classifier="A. GBM")
a_df_rf <- a_df %>%
  select(contains("rf")) %>% 
  rename(samples_cp=samples_cp_rf,
         samples_ncp=samples_ncp_rf) %>% 
  mutate(Classifier="B. RF")

g <- 
  a_df_gbm %>%
  bind_rows(a_df_rf) %>% 
  melt(id.vars="Classifier") %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("Centered", "Non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=20, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  facet_wrap(~Classifier)
# ggsave("../output/wide_data.pdf", g, width = 12, height = 8)

@@

full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star_gbm <- r_star(full_data, uncertainty = T, method="gbm")
r_star_rf <- r_star(full_data, uncertainty = T, method="rf")
a_df <- tibble(samples_400_gbm=r_star_gbm,
               samples_400_rf=r_star_rf)
saveRDS(a_df, "../output/mvt_wide_400_summary.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
```

@@

fit <- readRDS("../output/mvt_wide_1000.rds")
full_data <- rstan::extract(fit, permuted=F, inc_warmup=F)
r_star_gbm <- r_star(full_data, uncertainty = T, method="gbm")
r_star_rf <- r_star(full_data, uncertainty = T, method="rf")

a_df <- readRDS("../output/mvt_wide_400_summary.rds")
a_df <- a_df %>% 
    mutate(samples_1000_gbm=r_star_gbm,
           samples_1000_rf=r_star_rf)
saveRDS(a_df, "../output/mvt_wide_summaries.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
a_df <- readRDS("../output/mvt_wide_summaries.rds")
a_df_gbm <- a_df %>%
  select(contains("gbm")) %>% 
  rename(samples_1000cp=samples_cp_gbm,
         samples_ncp=samples_ncp_gbm) %>% 
  mutate(Classifier="A. GBM")
a_df_rf <- a_df %>%
  select(contains("rf")) %>% 
  rename(samples_cp=samples_cp_rf,
         samples_ncp=samples_ncp_rf) %>% 
  mutate(Classifier="B. RF")

a_df <- tibble(samples_400=a_df$.$samples_400, samples_1000=a_df$samples_1000)
g1 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400", "1000")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=20, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")
ggsave("../output/very_wide_data.pdf", g, width = 12, height = 8)
```
